Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-06-02 paper.tex
Werk

In practical terms, we build a system by using LibP2P and IPFS as libraries, and building a dynamically updating tree which contains metadata and pointers to hashes of files - which can then be retrieved over IPFS. We also outline some attacks a censor may take against IPFS, and we modify our usage of IPFS to mitigate these attacks. We build both Golang and Javascript libraries which are used to access and update the aformentioned tree, as well as to establish uplink channels. We build a benchmarking app on top of our network, as well as some demo apps [TODO: list final apps].

@@

Censorship circumvention has developed over several decades. Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems. The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\label{pt}\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.

@@

As various censorship apparatuses developed, DPI began being used. DPI caused issues for several protocols - as it was able to selectively censor unencrypted or partially encrypted data streams based on parameters that a censor sets. [TODO: xref DPI] OBFS2 was developed by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI. Obfs2 was vulnerable however, as a passive MitM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using. Active probing involves an adversary sending data of their choice to a server of their choice, and observing the response. They may potentially continue probing depending on the response. [TODO: Give an example] obfs2 was vulnerable to active probes as well.\footnote{And, indeed, it was actively probed by China.\cite{TODO https://gitlab.torproject.org/legacy/trac/-/issues/8591}}

@@

Snowflake took the concepts presented in Flashproxy and iterated on them and deployed them widely. Snowflake switched the transport in use from Websockets to WebRTC.\footnote{WebRTC is a commonly used standard across a variety of digital applications. Notably, it is supported in the web browser via Javascript. WebRTC is used for a variety of tasks, including video, audio, and other data, and is used by most video/audio chatting applications.} WebRTC was designed for P2P usage, and an ecosystem of utility protocols and standards has arisen around it, including tools to do NAT puncturing and establishing connections between users in various, differing networks, which provides significant utility to Snowflake compared to Websockets.\footnote{Snowflake uses Interactive Connectivity Establishment (ICE) to connect users behind NATs. ICE uses STUN and TURN relays as tools to ensure a connection can be established. STUN is commonly used and is available widely on the web, and is required for innocuous services to function as well. TURN services are less common, as they require significantly more infrastructure and are not generally permissionless like STUN.\cite{snowflake-tech}} Snowflake iterated on the rendezvous by creating a broker. The broker is reached by using a high-reliability, low-bandwidth channel (domain fronting in practice, see Section \ref{domain fronting} for further details). The broker is able to match volunteers and users to each other, in order to provide service. Snowflake then makes several usability improvements, setting up usage such that a client can fail over to a backup volunteer should their primary one fail, as well as maintaining a session across numerous volunteers using Turbotunnel.\footnote{Turbotunnel is a concept most completely implemented in Snowflake. It is a session/reliability layer that exists above an obfuscation layer.\cite{turbotunnel} Many transports exist above a reliability layer (e.g. obfs4 uses TCP), so adding an additional reliablilty layer adds notable overhead. In some cases, such as Snowflake, where the transports used are very unreliable, the benefits outweigh the costs. Turbotunnel also addresses several other issues - for example, a censor could close any long-running connections to disable obfs4.\cite{turbotunnel} Without any internal reliability layer, the connection must restart from scratch, effectively preventing usage of the transport, even if an adversary did not identify a specific bridge.}

@@

Massbrowser is a P2P circumvention system. Massbrowser was designed to address flaws of existing systems - specifically, that systems that rely on limited, well known bridges (such as obfs4) are easily blocked, [TODO: xref] certain systems are expensive (such as using domain fronting for a full web session), many systems offer poor quality of service due to poor scalability, several systems force a user to add additional overhead to their web session by using another tool such as Tor,\footnote{Many web users do not care about anonymity and would prefer simply to get around web blocks regardless of anonymity guarentees.} and many systems (particularly decoy routing) are difficult to deploy.\cite{massbrowser}

@@

On top of this, because proxies may be in censored regions, MassBrowser maintains a complex whitelist on a per proxy basis - if a proxy is in a censored region, it cannot acquire certain content for the connected circumvention user.\footnote{MassBrowser simply tunnels through Tor in this case - creating a chicken vs egg problem.} This is costly - measurements must be performed to maintain this whitelist, and it assumes accesibility to CacheBrowser and Tor, and the maintinence of this whitelist does not benefit from economies of scale. On top of this, proxy providers may heavily tailor the loads they wish to support, employing whitelisting, destination whitelisting (which varies from the basic whitelisting behavior previously mentioned), loads, and other options.\cite{massbrowser} On top of this, MassBrowser uses custom software - either GUI software or a modified version of Firefox.

@@

Most of the previously mentioned channels require either a shared secret (e.g. obfs4) or a rendezvous (e.g. snowflake). Distributing a secret or setting up a rendezvous cannot be punted indefinitely, and as such there must be a way to perform these actions, even in a censored region. High-reliability channels may be used for these actions. Though all high-reliability channels vary in numerous ways, they can generally be characterized as low-bandwidth, highly available, and sticky addresses. Each of these characteristics is important for differing reasons. Most of these channels are considered low-bandwidth - were they not, we could simply use the channel as the primary transport.\footnote{And, this can still be done, see section \ref{meek} for some discussion of using one for a full connection.} A channel must be highly available, or it could not be relied upon. Finally, sticky addresses (e.g. an email address, a social media handle) are important, as a more temporary address would leave us punting on distributing a secret or setting up a rendezvous channel - a sticky address allows one (or several) addresses to be hard-coded in a transports default config for the long run, allowing for usage without acquiring more info out-of-band.

@@

Domain fronting arose through exploiting the differences between the plaintext and encrypted portions of an HTTPS connection sequence. Though implementation varies slightly depending on the provider, at a high level domain fronting is accomplished by setting up a server behind the networks of a key piece of internet infrastructure,\footnote{Usually large providers of either direct services (e.g. Google) or CDNs (e.g. Cloudflare).} and initializing DNS and server name indication (SNI) using a whitelisted domain from that same provider. After that, the HTTP host header is set to the proper destination (as this field is encrypted by TLS, the censor is unable to see it). Domain fronting is relatively simple to setup, and does not require direct participation from the provider (though, they cannot explicitly disallow it).\cite{domain fronting} Domain fronting is used extensively, from full sessions,\cite{meek} to bootstrapping in Snowflake, or passing out of band secrets for Obfs4.

@@

Sweet introduced the concept of channels with high availability guarentees. Sweet chooses to use email to build on the concepts presented in "The Parrot is Dead" by Housmandr et al.\cite{parrot} Using the email protocol properly is trivial to do given the wide variety of available codebases and the numerous email servers in existence on the web. Sweet tunnels a full connection via email - however, it comes with increased latencies as a result. Sweet is explicitly vulnerable to traffic analysis, as most users do not tunnel a full web connection via email.\cite{sweet}

@@

In reality, no censors appear to be doing behavioral analysis of web traffic - however, that does not mean they could not start doing so. In reality, it's likely that email could be used in a manner more strict than Sweet and less strict than Raven for small messages correlated with a real person accessing a system - ie, when a user is actually touching their web browser, shooting off and recieving a few email might not conform to a precisely real behavior, but it might be close enough that a censor could not detect it without significant false positives causing the blocking of regular email traffic.

In the real world, Tor uses email as a channel for distributing obfs4 bridges. This works to succesfully provide users with bridges, though this runs into the bridge distribution problem limiting effectiveness, discussed in \ref{distribution}.

@@

[TODO - a bunch of case studies]

@@

\subsection{Real world and academic theory}

@@

@@

[TODO - Salmon + that followup paper]

@@

Peer to peer networking has existed since the early web, but has fallen into and out of favor over time. The web was originally envisioned as many small networks interlinking to form the full web, but as the internet developped, many services such as email, web hosting, server provision, etc. have become centralized by large companies. For example, if two users message on a site like Twitter, their messages are going to Twitter, being stored on Twitter, and passed to the recipient via Twitter, rather than directly (even if both users have no desire for Twitter to have access to the content). Generally, unless a user is delibrately using a specific P2P protocol, only select activities are augmented with P2P connections (usually voice/videochat and gaming). The most notable uses of P2P networks are torrents, some cryptocurrencies, and IPFS.

@@

BitTorrent originated in 2001.\footnote{We use torrent and BitTorrent interchangebly throughout this paper.} It was designed to make provision of common, large files more effecient. "When a file is made available using HTTP, all upload cost is placed on the hosting machine. With BitTorrent, when multiple people are downloading the same file at the same time, they upload pieces of the file to each other. This redistributes the cost of upload to downloaders, (where it is often not even metered), this making hosting a file with a potentially unlimited number of downloaders affordable."\cite{torrent} Publishers of files choose to make their file available as a torrent, where anyone with the proper software can download it.\footnote{Nowadays, even web browsers can use extensions to access torrents.\cite{webtorrent}} At launch, users would make .torrent files available - these files contained basic info about a file - the size, name, a tracker,\footnote{"Trackers are responsible for helping downloaders find each other. They speak a very simple protocol layered on top of HTTP in which a downloader sends information about what file it’s downloading, what port it’s listening on, and similar information, and the tracker responds with a list of contact information for peers which are downloading the same file."\cite{torrent}} and hashing info.\footnote{Since then, magnet links have become an option as well. These are specifically formatted links that provide the data needed to bootstrap a torrent download without pulling a file separate from the magnet link.}\cite{torrent} The original uploader must send out at least one copy of the file being shared (or it must already be distributed out of band), but after that, the file can be reconstructed from anyone sharing the torrent rather than the original provider. Users acquire peers in a random manner from trackers, ensuring robustness. Bittorrent divides files into small pieces of fixed size, which allows users to upload before a download is completed, and these pieces are known via their SHA1 hash, ensuring file integrity. Peers announce what files they have, resulting "in less than a tenth of a percent bandwidth overhead [while] reliably utiliz[ing] all available upload capacity.\cite{torrent} BitTorrent generally prioritizes the "rarest" pieces of a file first, based upon which peers have which pieces.\footnote{Though, users can customize the ordering if they choose to do so. Selecting the rarest first both ensures a full file is available, and it maximizes the sharing speed of a torrent, as once the rarest piece is acquired by a second peer, that peer can share that piece further.} BitTorrent reaches a relatively optimum end result through a mechanism known as choking: BitTorrent downloads from several peers - the fastest known peers - and optimistically probes for faster peers as well.\cite{torrent} BitTorrent effectively uses "tit-for-tat" exchange mechanisms to allow for a relatively distributed system which generally reaches optimal or near-optimal outcomes.

@@

IPFS is a P2P system where files are shared based on the content of the files, rather than URLs (uniform resource locaters). URLs point to specific locations, which may host whatever those in charge of the location choose to serve, assuming you can route to the specific location to acquire a file.\footnote{Routing to blocked content is indeed the primary problem that we seek to solve in the censorship circumvention sphere.} Users of IPFS (either directly or an app that performs content acquisition under the hood using IPFS) request specific files, based upon the hash of the files. A key assumption of IPFS is that no nodes are priveleged or trusted specially, which leads to several design decisions based upon prior work. At it's core, IPFS provides basic utilities for identities, networking, routing, file exchange, object acquisition, file ststem management, and basic naming capabilities.\cite{ipfs}

A node in IPFS can be thought of as having an identity.\footnote{This identity can be refreshed as often as a user wants, though there is some benefit to using the same identity in the long run.} This identity is very basic: it's simply a lone node ID, which is the hash of a nodes public key. These keys are built using primitives from the S/Kademlia DHT.\footnote{S/Kademlia is an iteration of the Kademlia DHT. Kademlia DHT is designed to minimize the number of hops needed to learn the location of a desired address.\cite{kademlia} A large network of 10,000,000 nodes could be searched with 20 hops on average - queries are resolved in $\lceil log_2(n) \rceil$, where $n$ is the number of nodes in the network.\cite{ipfs} Additionally, Kademlia has low overhead for control messages, and had prior large usage.\cite{ipfs} S/Kademlia builds on Kademlia to reduce Sybil attacks by requiring some proof of work work (signatures) and allows for lookups in a more adversarial network - "S/Kademlia achieves a [lookup success] rate of .85 even with an adversarial fraction as large as half of the nodes."\cite{ipfs} S/Kademlia assumes an adversary similar to one which we do - an adversary can manipulate packets, do observation, etc. They can also generate an arbitrary number of adversarial nodes, and might attempt an eclipse attack.\cite{skademlia} The proof of work for generating a node-id is based upon putting some basic constraints on node-ids (e.g. certain bits must be 0), and therfore generating a valid node-id is doable for users, but is a configurable variable to stop an adversary.\cite{skademlia}} IPFS is designed to be transport agnostic - this is done using a \emph{multiaddr}, which is an identifier similar to a URL in terms of hierarchy, but providing networking information. For routing, IPFS must allow nodes to find other peers, and the location of specific content. IPFS draws on S/Kademlia and Coral DSHT's (distributed sloppy hash table) extensions to Kademlia for this - Coral DSHT notably reduces the overhead needed to find content by allowing for acquisition of just a single peer to acquire content, rather than needing to acquire every peer (hence, the \emph{sloppy} in the name). Coral also organizes content into clusters, which allows for more focused searching for content and reducing the latency of the network.

Content acquisition builds on BitTorrent. (See Section \ref{torrent} for more.) IPFS effectively uses the file sharing technology of torrenting, but instead of focusing on the pieces contained in a singular torrent, IPFS simply annonces all pieces it has, regardless of the original file. This means that files which share content may be acquired from multiple users, even if they don't have the exact same file as the user looking for the content (e.g. a user may be seeking a music album, but they may acquire a song from that album from a user who only has that song). A notable change from BitTorrent, BitSwap (the name of the content swapping protocol of IPFS) also encourages acquisition of generally rare files that users want, as by decoupling desired files from a torrent, users are incentivized to provide content that providers of the content they want are in search of, which results in a spread of rarer, more desired files in order to recieve better download speeds.\cite{ipfs}

IPFS builds a Merkle DAG on top of the DHT and content swapping technology. This DAG links via hashes of content - a generalization of the Git data structure.\cite{ipfs} Using this dag of hashes, IPFS has \emph{unique} identification of any objects, it is tamper resistent, and it allows for easy deduplication.\cite{ipfs} Content can be acquired using a very basic path format: /ipfs/<HASH>/<PATH TO OBJECT>. This format allows for easy integration into existing file systems, and for minor changes to allow for web browser usage (set up as: ipfs://<HASH>/<PATH TO OBJECT>). Users can add any object to the DHT, and may choose to \emph{pin} an object - marking it as an object that should be kept for the long run. Files are represented similar to Git files, with some minor additions added to improve performance. These changes include fast size lookups, deduplication of large files, and organizing commits into a tree.\cite{ipfs} A Git object can actually be converted to IPFS without losing any info, but not vice-versa.

@@

IPFS has been in use for several years, and has been used to run some services and provide some data on the web. [TODO: any censorship circumvention uses?] It has been implemented in both Golang and Javascript (with other languages in various states of completion), and is available in some prominent web browsers (Brave and Opera).\cite{ipfs-measure} The current version of IPFS uses a CID (content identifier) to point to objects - this is a variant of the hashes used to point to object. These CIDs include a multibase prefix - a prefix used to indicate the base the encoding used, a version identifier, a codec identifier (e.g. protobuf, JSON, etc), and a \emph{multihash} - a hah that indicates the hash algorithm used, and the length of the hash.\cite{ipfs-measure} IPFS uses a multiaddress to provide network addresses of peers - a flexible structure that allows conveying a full network address by first outlining the peer, their network protocol (and any data needed to use), the transport layer, and any additional transports that may reside on top of that.\cite{ipfs-measure} A couple sample multiaddresses are /ip4/<ip address>/tcp/<PORT>/ipfs/<Node ID> and /dns4/site.com/tcp/<PORT>/tls/ipfs/<Node ID>.

>>>>

In practical terms, we build a system by using LibP2P and IPFS as libraries, and building a dynamically updating tree which contains metadata and pointers to hashes of files - which can then be retrieved over IPFS. We also outline some attacks a censor may take against IPFS, and we modify our usage of IPFS to mitigate these attacks. We build both Golang and Javascript libraries which are used to access and update the aforementioned tree, as well as to establish uplink channels. We build a benchmarking app on top of our network, as well as some demo apps [TODO: list final apps].

@@

Censorship circumvention has developed over several decades. Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems. The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\label{pt}\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence. Additionally, observing real world censors are frequently observed to see how theory plays out in the real world, as well as if other censorship techniques are in place that have not been suggested in the literature, or were not significantly explored in the literature. We discuss real world observations and censorship techniques in \ref{real}.

@@

As various censorship apparatuses developed, DPI began being used. DPI caused issues for several protocols - as it was able to selectively censor unencrypted or partially encrypted data streams based on parameters that a censor sets. [TODO: xref DPI] obfs2 was developed by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI. Obfs2 was vulnerable however, as a passive MitM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using. Active probing involves an adversary sending data of their choice to a server of their choice, and observing the response. They may potentially continue probing depending on the response. [TODO: Give an example] obfs2 was vulnerable to active probes as well.\footnote{And, indeed, it was actively probed by China.\cite{TODO https://gitlab.torproject.org/legacy/trac/-/issues/8591}}

@@

Snowflake took the concepts presented in Flashproxy and iterated on them and deployed them widely. Snowflake switched the transport in use from Websockets to WebRTC.\footnote{WebRTC is a commonly used standard across a variety of digital applications. Notably, it is supported in the web browser via Javascript. WebRTC is used for a variety of tasks, including video, audio, and other data, and is used by most video/audio chatting applications.} WebRTC was designed for P2P usage, and an ecosystem of utility protocols and standards has arisen around it, including tools to do NAT puncturing and establishing connections between users in various, differing networks, which provides significant utility to Snowflake compared to Websockets.\footnote{Snowflake uses Interactive Connectivity Establishment (ICE) to connect users behind NATs. ICE uses STUN and TURN relays as tools to ensure a connection can be established. STUN is commonly used and is available widely on the web, and is required for innocuous services to function as well. TURN services are less common, as they require significantly more infrastructure and are not generally permissionless like STUN.\cite{snowflake}} Snowflake iterated on the rendezvous by creating a broker. The broker is reached by using a high-reliability, low-bandwidth channel (domain fronting in practice, see Section \ref{domain fronting} for further details). The broker is able to match volunteers and users to each other, in order to provide service. Snowflake then makes several usability improvements, setting up usage such that a client can fail over to a backup volunteer should their primary one fail, as well as maintaining a session across numerous volunteers using Turbotunnel.\footnote{Turbotunnel is a concept most completely implemented in Snowflake. It is a session/reliability layer that exists above an obfuscation layer.\cite{turbotunnel} Many transports exist above a reliability layer (e.g. obfs4 uses TCP), so adding an additional reliability layer adds notable overhead. In some cases, such as Snowflake, where the transports used are very unreliable, the benefits outweigh the costs. Turbotunnel also addresses several other issues - for example, a censor could close any long-running connections to disable obfs4.\cite{turbotunnel} Without any internal reliability layer, the connection must restart from scratch, effectively preventing usage of the transport, even if an adversary did not identify a specific bridge.}

@@

Massbrowser is a P2P circumvention system. Massbrowser was designed to address flaws of existing systems - specifically, that systems that rely on limited, well known bridges (such as obfs4) are easily blocked, [TODO: xref] certain systems are expensive (such as using domain fronting for a full web session), many systems offer poor quality of service due to poor scalability, several systems force a user to add additional overhead to their web session by using another tool such as Tor,\footnote{Many web users do not care about anonymity and would prefer simply to get around web blocks regardless of anonymity guarantees.} and many systems (particularly decoy routing) are difficult to deploy.\cite{massbrowser}

@@

On top of this, because proxies may be in censored regions, MassBrowser maintains a complex whitelist on a per proxy basis - if a proxy is in a censored region, it cannot acquire certain content for the connected circumvention user.\footnote{MassBrowser simply tunnels through Tor in this case - creating a chicken vs egg problem.} This is costly - measurements must be performed to maintain this whitelist, and it assumes accessibility to CacheBrowser and Tor, and the maintinence of this whitelist does not benefit from economies of scale. On top of this, proxy providers may heavily tailor the loads they wish to support, employing whitelisting, destination whitelisting (which varies from the basic whitelisting behavior previously mentioned), loads, and other options.\cite{massbrowser} On top of this, MassBrowser uses custom software - either GUI software or a modified version of Firefox.

@@

Most of the previously mentioned channels require either a shared secret (e.g. obfs4) or a rendezvous (e.g. snowflake). Distributing a secret or setting up a rendezvous cannot be punted indefinitely, and as such there must be a way to perform these actions, even in a censored region. High-reliability channels may be used for these actions. Though all high-reliability channels vary in numerous ways, they can generally be characterized as low-bandwidth, highly available, and sticky addresses. Each of these characteristics is important for differing reasons. Most of these channels are considered low-bandwidth - were they not, we could simply use the channel as the primary transport.\footnote{And, this can still be done, see section \ref{meek} for some discussion of using one for a full connection.} A channel must be highly available, or it could not be relied upon. Finally, sticky addresses (e.g. an email address, a social media handle) are important, as a more temporary address would leave us punting on distributing a secret or setting up a rendezvous channel - a sticky address allows one (or several) addresses to be hard-coded in a transports default configuration for the long run, allowing for usage without acquiring more info out-of-band.

@@

Domain fronting arose through exploiting the differences between the plaintext and encrypted portions of an HTTPS connection sequence. Though implementation varies slightly depending on the provider, at a high level domain fronting is accomplished by setting up a server behind the networks of a key piece of internet infrastructure,\footnote{Usually large providers of either direct services (e.g. Google) or CDNs (e.g. Cloudflare).} and initializing DNS and server name indication (SNI) using a whitelisted domain from that same provider. After that, the HTTP host header is set to the proper destination (as this field is encrypted by TLS, the censor is unable to see it). Domain fronting is relatively simple to setup, and does not require direct participation from the provider (though, they can explicitly disallow it).\cite{domain fronting} Domain fronting is used extensively, from full sessions,\cite{meek} to bootstrapping in Snowflake, or passing out of band secrets for Obfs4.

@@

Sweet introduced the concept of channels with high availability guarantees. Sweet chooses to use email to build on the concepts presented in "The Parrot is Dead" by Housmandr et al.\cite{parrot} Using the email protocol properly is trivial to do given the wide variety of available codebases and the numerous email servers in existence on the web. Sweet tunnels a full connection via email - however, it comes with increased latencies as a result. Sweet is explicitly vulnerable to traffic analysis, as most users do not tunnel a full web connection via email.\cite{sweet}

@@

In reality, no censors appear to be doing behavioral analysis of web traffic - however, that does not mean they could not start doing so. In reality, it's likely that email could be used in a manner more strict than Sweet and less strict than Raven for small messages correlated with a real person accessing a system - IE, when a user is actually touching their web browser, shooting off and receiving a few email might not conform to a precisely real behavior, but it might be close enough that a censor could not detect it without significant false positives causing the blocking of regular email traffic.

In the real world, Tor uses email as a channel for distributing obfs4 bridges. This works to successfully provide users with bridges, though this runs into the bridge distribution problem limiting effectiveness, discussed in \ref{distribution}.

@@

[TODO - a bunch of case studies - lox has several]

@@

\subsection{Observing adversaries}

@@

\subsubsection{Attacks on specific channels}

@@

[This subsection is being substatially revised]

We have discussed how channels work on the wire, and how specific protocols may be blocked, but we've deferred discussing the main problem with how many transports like obfs are frequently blocked: an adversary attempts to pose as a non-malicious user and requests access to an obfs bridge. They then attempt to probe the bridge, and if the connection succeeds, they block the bridge. This can be done quickly and easily by an adversary with resources, allowing for the blocking of numerous bridges if no countermeasures are put in place. This problem arises because connection info must be disseminated to users who have no connection to those providing the circumvention techniques. There is no trust and effectively no communication between the parties. Circumvention must allow all users, even those who do not have technical contacts in areas where the internet is not censored, to access the web to succeed. We term this problem \emph{the bridge distribution problem}.

Salmon, proposed by Douglas et al., formalized this notion of bridge distribution

, and formulated one potential solution.\cite{distribution} Nasr et al build on the \emph{college admissions game} framework - a framework used in game theory to analyze and optimize solutions to certain problems of a certain form. The game is formulated such that there are effectively two entities - the bridge distributor, and the adversary. Nasr et al. show that the optimal distribution strategy is to provide clients with arbitrary proxies, but then track which clients request proxies again, and then new proxies are distributed based upon the \emph{deferred acceptance algorithm}. This is done until all bridges are full or all clients have a bridge and are no longer requesting bridges.\cite{distribution} The authors then show that an optimal censor will attempt to enumerate bridges, but will delay blocking a bridge to observe it for some time. The authors then demonstrate several bridge distributions strategies, but ultimately conclude that if new bridges do not come online often enough, then a censor will inevitably be able to block the full network of proxies.\cite{distribution}

[TODO: Fix the above]

Lox, by Tulloch and Goldberg, builds on Salmon by introducing a social graph based bridge-distribution scheme. They also provide protection for the topology of the social network used.\cite{lox} 
[TODO - Salmon + that followup paper]

@@

Peer to peer networking has existed since the early web, but has fallen into and out of favor over time. The web was originally envisioned as many small networks interlinking to form the full web, but as the internet developed, many services such as email, web hosting, server provision, etc. have become centralized by large companies. For example, if two users message on a site like Twitter, their messages are going to Twitter, being stored on Twitter, and passed to the recipient via Twitter, rather than directly (even if both users have no desire for Twitter to have access to the content). Generally, unless a user is deliberately using a specific P2P protocol, only select activities are augmented with P2P connections (usually voice/videochat and gaming). The most notable uses of P2P networks are torrents, some cryptocurrencies, and IPFS.

@@

BitTorrent originated in 2001.\footnote{We use torrent and BitTorrent interchangeably throughout this paper.} It was designed to make provision of common, large files more efficient. "When a file is made available using HTTP, all upload cost is placed on the hosting machine. With BitTorrent, when multiple people are downloading the same file at the same time, they upload pieces of the file to each other. This redistributes the cost of upload to downloaders, (where it is often not even metered), this making hosting a file with a potentially unlimited number of downloaders affordable."\cite{torrent} Publishers of files choose to make their file available as a torrent, where anyone with the proper software can download it.\footnote{Nowadays, even web browsers can use extensions to access torrents.\cite{webtorrent}} At launch, users would make .torrent files available - these files contained basic info about a file - the size, name, a tracker,\footnote{"Trackers are responsible for helping downloaders find each other. They speak a very simple protocol layered on top of HTTP in which a downloader sends information about what file it’s downloading, what port it’s listening on, and similar information, and the tracker responds with a list of contact information for peers which are downloading the same file."\cite{torrent}} and hashing info.\footnote{Since then, magnet links have become an option as well. These are specifically formatted links that provide the data needed to bootstrap a torrent download without pulling a file separate from the magnet link.}\cite{torrent} The original uploader must send out at least one copy of the file being shared (or it must already be distributed out of band), but after that, the file can be reconstructed from anyone sharing the torrent rather than the original provider. Users acquire peers in a random manner from trackers, ensuring robustness. BitTorrent divides files into small pieces of fixed size, which allows users to upload before a download is completed, and these pieces are known via their SHA1 hash, ensuring file integrity. Peers announce what files they have, resulting "in less than a tenth of a percent bandwidth overhead [while] reliably utiliz[ing] all available upload capacity.\cite{torrent} BitTorrent generally prioritizes the "rarest" pieces of a file first, based upon which peers have which pieces.\footnote{Though, users can customize the ordering if they choose to do so. Selecting the rarest first both ensures a full file is available, and it maximizes the sharing speed of a torrent, as once the rarest piece is acquired by a second peer, that peer can share that piece further.} BitTorrent reaches a relatively optimum end result through a mechanism known as choking: BitTorrent downloads from several peers - the fastest known peers - and optimistically probes for faster peers as well.\cite{torrent} BitTorrent effectively uses "tit-for-tat" exchange mechanisms to allow for a relatively distributed system which generally reaches optimal or near-optimal outcomes.

@@

IPFS is a P2P system where files are shared based on the content of the files, rather than URLs (uniform resource locators). URLs point to specific locations, which may host whatever those in charge of the location choose to serve, assuming you can route to the specific location to acquire a file.\footnote{Routing to blocked content is indeed the primary problem that we seek to solve in the censorship circumvention sphere.} Users of IPFS (either directly or an app that performs content acquisition under the hood using IPFS) request specific files, based upon the hash of the files. A key assumption of IPFS is that no nodes are privileged or trusted specially, which leads to several design decisions based upon prior work. At it's core, IPFS provides basic utilities for identities, networking, routing, file exchange, object acquisition, file system management, and basic naming capabilities.\cite{ipfs}

A node in IPFS can be thought of as having an identity.\footnote{This identity can be refreshed as often as a user wants, though there is some benefit to using the same identity in the long run.} This identity is very basic: it's simply a lone node ID, which is the hash of a nodes public key. These keys are built using primitives from the S/Kademlia DHT.\footnote{S/Kademlia is an iteration of the Kademlia DHT. Kademlia DHT is designed to minimize the number of hops needed to learn the location of a desired address.\cite{kademlia} A large network of 10,000,000 nodes could be searched with 20 hops on average - queries are resolved in $\lceil log_2(n) \rceil$, where $n$ is the number of nodes in the network.\cite{ipfs} Additionally, Kademlia has low overhead for control messages, and had prior large usage.\cite{ipfs} S/Kademlia builds on Kademlia to reduce Sybil attacks by requiring some proof of work work (signatures) and allows for lookups in a more adversarial network - "S/Kademlia achieves a [lookup success] rate of .85 even with an adversarial fraction as large as half of the nodes."\cite{ipfs} S/Kademlia assumes an adversary similar to one which we do - an adversary can manipulate packets, do observation, etc. They can also generate an arbitrary number of adversarial nodes, and might attempt an eclipse attack.\cite{skademlia} The proof of work for generating a node-id is based upon putting some basic constraints on node-ids (e.g. certain bits must be 0), and therefore generating a valid node-id is doable for users, but is a configurable variable to stop an adversary.\cite{skademlia}} IPFS is designed to be transport agnostic - this is done using a \emph{multiaddr}, which is an identifier similar to a URL in terms of hierarchy, but providing networking information. For routing, IPFS must allow nodes to find other peers, and the location of specific content. IPFS draws on S/Kademlia and Coral DSHT's (distributed sloppy hash table) extensions to Kademlia for this - Coral DSHT notably reduces the overhead needed to find content by allowing for acquisition of just a single peer to acquire content, rather than needing to acquire every peer (hence, the \emph{sloppy} in the name). Coral also organizes content into clusters, which allows for more focused searching for content and reducing the latency of the network.

Content acquisition builds on BitTorrent. (See Section \ref{torrent} for more.) IPFS effectively uses the file sharing technology of torrenting, but instead of focusing on the pieces contained in a singular torrent, IPFS simply announces all pieces it has, regardless of the original file. This means that files which share content may be acquired from multiple users, even if they don't have the exact same file as the user looking for the content (e.g. a user may be seeking a music album, but they may acquire a song from that album from a user who only has that song). A notable change from BitTorrent, BitSwap (the name of the content swapping protocol of IPFS) also encourages acquisition of generally rare files that users want, as by decoupling desired files from a torrent, users are incentivized to provide content that providers of the content they want are in search of, which results in a spread of rarer, more desired files in order to receive better download speeds.\cite{ipfs}

IPFS builds a Merkle DAG on top of the DHT and content swapping technology. This DAG links via hashes of content - a generalization of the Git data structure.\cite{ipfs} Using this dag of hashes, IPFS has \emph{unique} identification of any objects, it is tamper resistant, and it allows for easy deduplication.\cite{ipfs} Content can be acquired using a very basic path format: /ipfs/<HASH>/<PATH TO OBJECT>. This format allows for easy integration into existing file systems, and for minor changes to allow for web browser usage (set up as: ipfs://<HASH>/<PATH TO OBJECT>). Users can add any object to the DHT, and may choose to \emph{pin} an object - marking it as an object that should be kept for the long run. Files are represented similar to Git files, with some minor additions added to improve performance. These changes include fast size lookups, deduplication of large files, and organizing commits into a tree.\cite{ipfs} A Git object can actually be converted to IPFS without losing any info, but not vice-versa.

@@

IPFS has been in use for several years, and has been used to run some services and provide some data on the web. [TODO: any censorship circumvention uses?] It has been implemented in both Golang and Javascript (with other languages in various states of completion), and is available in some prominent web browsers (Brave and Opera).\cite{ipfs-measure} The current version of IPFS uses a CID (content identifier) to point to objects - this is a variant of the hashes used to point to object. These CIDs include a multibase prefix - a prefix used to indicate the base the encoding used, a version identifier, a codec identifier (e.g. protobuf, JSON, etc), and a \emph{multihash} - a hash that indicates the hash algorithm used, and the length of the hash.\cite{ipfs-measure} IPFS uses a multiaddress to provide network addresses of peers - a flexible structure that allows conveying a full network address by first outlining the peer, their network protocol (and any data needed to use), the transport layer, and any additional transports that may reside on top of that.\cite{ipfs-measure} A couple sample multiaddresses are /ip4/<ip address>/tcp/<PORT>/ipfs/<Node ID> and /dns4/site.com/tcp/<PORT>/tls/ipfs/<Node ID>.
